---
title: "Statistics Week 1"
author: "Ronald Dijks"
date: "9/22/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### 1.a. Write an expression to compute the sum of the number 3 and 4.
```{r}
3 + 4
```

### 1.b. Write an expression to determine if the product of 4 and 5 is equal to 21.
```{r}
4 * 5 == 21
```

### 1.c. Create the variables x, y, z with the values (2, 3.5, 7).
```{r}
x = 2
y = 3.5
z = 7
```

### 1.d. Exploit a function of R to investigate the datatype of the three variables x, y, z.
```{r}
str(x)
str(y)
str(z)
```

### 1.e. Write an expression to compute the multiplication of the three variables x, y, z.
```{r}
x * y * z
```

### 1.f. Write a boolean expression which checks if the product of x,y,z is equal to 49.
```{r}
x * y * z == 49
```

### 1.g. Create a variable s with the value "Alexander"
```{r}
s = "Alexander"
```

### 1.h. Look for a function returning the length of a string and use it to determine the length of s.
```{r}
nchar(s)
```

## Exercise 2

### 2.a. Create a variable x with the value 1 trough 10.
```{r}
x = 1:10
```

### 2.b. How can you investigate the length of x?
```{r}
length(x)
```

### 2.c. Multiply x by the number '1.2'.
```{r}
x * 1.2
```

### 2.d. Multiply the first five elements of x by 2.
```{r}
c(x[1:5] * 2, x[6:10])
```

### 2.e. Visualize x using barplot(x).
```{r}
barplot(x)
```

### 2.f. Assign to x the values of all integers from 0 to 10.
```{r}
x = 0:9
```

### 2.g. Create a graph of x against x useing plot(x, x, type="b")
```{r}
plot(x, x, type = "b")
```

### 2.h. Use plot to draw the graph of the function 'y=3x+2' for the values of x between 0 and 10.
```{r}
x = 1:9
plot(x, 3*x+2)
```

### 2.i. Use plot to draw the graph of the function 'y=sin(x)' for the values of x between 0 and (2*PI) (use atleast 200 points).
```{r}
x = seq(0, 2*pi, length.out = 200)
plot(x, sin(x))
```

### 2.j. Find out how the graph can be made of only one line (without symbols) and give the graph a
name (for example "My first R Graph").
```{r}
plot(
  x, 
  sin(x), 
  main = "My first R Graph",
  type = "l"
)
```

### 2.k. Find out how the function curve works and use it to plot the values of cos(x) between 0 and 2PI.
```{r}
curve(cos, 0, 2*pi, n=200)
```