---
title: "Statistics Week 1"
author: "Ronald Dijks"
date: "9/22/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1

### 1.a. Write an expression to compute the sum of the number 3 and 4.
```{r}
3 + 4
```

### 1.b. Write an expression to determine if the product of 4 and 5 is equal to 21.
```{r}
4 * 5 == 21
```

### 1.c. Create the variables x, y, z with the values (2, 3.5, 7).
```{r}
x = 2
y = 3.5
z = 7
```

### 1.d. Exploit a function of R to investigate the datatype of the three variables x, y, z.
```{r}
str(x)
str(y)
str(z)
```

### 1.e. Write an expression to compute the multiplication of the three variables x, y, z.
```{r}
x * y * z
```

### 1.f. Write a boolean expression which checks if the product of x,y,z is equal to 49.
```{r}
x * y * z == 49
```

### 1.g. Create a variable s with the value "Alexander"
```{r}
s = "Alexander"
```

### 1.h. Look for a function returning the length of a string and use it to determine the length of s.
```{r}
nchar(s)
```

# Exercise 2

### 2.a. Create a variable x with the value 1 trough 10.
```{r}
x = 1:10
```

### 2.b. How can you investigate the length of x?
```{r}
length(x)
```

### 2.c. Multiply x by the number '1.2'.
```{r}
x * 1.2
```

### 2.d. Multiply the first five elements of x by 2.
```{r}
c(x[1:5] * 2, x[6:10])
```

### 2.e. Visualize x using barplot(x).
```{r}
barplot(x)
```

### 2.f. Assign to x the values of all integers from 0 to 10.
```{r}
x = 0:9
```

### 2.g. Create a graph of x against x useing plot(x, x, type="b")
```{r}
plot(x, x, type = "b")
```

### 2.h. Use plot to draw the graph of the function 'y=3x+2' for the values of x between 0 and 10.
```{r}
x = 1:9
plot(x, 3*x+2)
```

### 2.i. Use plot to draw the graph of the function 'y=sin(x)' for the values of x between 0 and (2*PI) (use atleast 200 points).
```{r}
x = seq(0, 2*pi, length.out = 200)
plot(x, sin(x))
```

### 2.j. Find out how the graph can be made of only one line (without symbols) and give the graph a
name (for example "My first R Graph").
```{r}
plot(
  x, 
  sin(x), 
  main = "My first R Graph",
  type = "l"
)
```

### 2.k. Find out how the function curve works and use it to plot the values of cos(x) between 0 and 2PI.
```{r}
curve(cos, 0, 2*pi, n=200)
```

# Exercise 3

### 3.a. Read the dataset Ozone into a variable called "air".
```{r}
setwd("/home/ronald/minor/CMIBOD021T_statistics/exercises")
air = read.csv("ozone.csv")
```

### 3.b. Which type of object is air?
```{r}
str(air)
```

### 3.c. What are the names of the columns of air?
```{r}
colnames(air)
```

### 3.d. From how many lines is air composed?
```{r}
nrow(air)
```

### 3.e. In some cells you see the value "NA", what does this mean?
NA stands for `Not Available`. This is a value that gets used when R cannot parse a value or the value is missing.

### 3.f. Try to compute the average ozone level using the mean command, why is the result NA?
Because NA is not a number, and thus you cannot compute a significant value from any calculation that includes NA.

### 3.g. Find out how to exclude NA values from the computation.
By using the `na.rm` argument on the `mean` function.

### 3.h. Compute the mean temperature of the dataset.
```{r}
mean(air$Temp, na.rm = TRUE)
```

### 3.i. How many observations of the dataset have a temperature strictly less than 67 and how many have one greater of equal to 67?
```{r}
obsLess = sum(air$Temp < 67)
obsLess
obsGreater = sum(air$Temp >= 67)
obsGreater
```

### 3.j. Create a vector "hot" with booleans corresponding to the temperatures that are higher than 80 Fahrenheit. Use this to split the Ozone dataset in two, the hot days and the cold days.
```{r}
hot = air$Temp > 80
hotDays = subset(air, Temp > 80)
coldDays = subset(air, Temp <= 80)
```

### 3.k. Determinethe mean ozone levels of warm days and cold days.
```{r}
mean(hotDays$Ozone, na.rm = T)
mean(coldDays$Ozone, na.rm = T)
```

### 3.l. Produce a plot containing the two boxplots of ozone levels.
```{r}
hotDays$Kind <- rep("Hot", nrow(hotDays))
coldDays$Kind <- rep("Cold", nrow(coldDays))
allDays = rbind(hotDays, coldDays)

boxplot(Temp~Kind, allDays)
```
